% !TeX root = Thesis.tex

\chapter{Method}
\label{chap:method}

This chapter presents the data-processing, architecture and training of the CSG-CRN model at a theoretical level.


\section{Input~Shape~Representation}
\label{sec:input_shape_representation}

CSG-CRN takes SDF point clouds as input. The format consists a set of query points $p \in \mathbb{R}^3$ and the corresponding signed distance value to the represented surface. This format was chosen to facilitate an efficient and differentiable method of discretizing implicit SDFs. Since CSG-CRN is a cascaded refinement network, the implicit SDF output needs to be discretized and reused as the next input to the network. 

Early versions of the architecture that only provided the target shape and current reconstruction volumes resulted in poor results. We found that the model performs better when given more context on which parts of the reconstruction need to be improved. This is accomplished by applying boolean operations to the target and reconstruction shapes to compute the missing, filled, and excess volumes. The same query points are used for all volume and the boolean operations are applied to the distance values.

The missing volume is found by subtracting the reconstruction from the target
\[d_{missing}=\max(d_target, -d_recon).\]

The filled volume is found by intersecting both the target and reconstruction
\[d_{filled}=\max(d_target, d_recon).\]

The excess volume is found by subtracting the target from the reconstruction
\[d_{excess}=\max(-d_target, d_recon).\]

The query points and the three distance values are combined to form a six-dimensional input vector.

\[input = [p, d_{missing}, d_{filled}, d_{excess}]\]


\section{Point~Sampling}
\label{sec:point_sampling}

Previous work~\cite{Genova2019} demonstrates that the method used to collect point samples for a loss function impacts the reconstruction accuracy of the model. A uniformly sampled point cloud evenly encompassing the operational bounds leads the model to omit thin structures and fine details. A point cloud containing only samples near to the target surface will result in better surface detail but worse volumetric accuracy further away from the surface. \cite{Genova2019} takes a hybrid approach by computing the loss function twice; once using uniformly sampled points and once using points sampled near the surface of the target shape. The two loss values are weighted and summed to create a loss function that achieves both good volumetric and surface accuracy.

We apply a similar approach when sampling query points for both our model input and loss function. The dataset contains a large number of uniformly sampled query points and distance values for each input shape sample. Using a heuristic algorithm, a subset of the uniform samples are filtered based on their distance to either the target or reconstruction surfaces to produce a near-surface point cloud. The near-surface point cloud is combined with more uniform point samples at a configured ratio and shuffled to form the input point cloud.


\section{Encoder~Network}
\label{sec:encoder_network_method}

Early designs for the CSG-CRN architecture included a self-supervised Siamese network to encode the difference in features between the target shape and initial reconstruction inputs. The shape samples are encoded separately by two identical networks that share network weights. The resultant latent vectors are processed by an intermediary fully-connected layer to find similarities and differences in the inputs and encode for the next shape prediction. This architecture has been successfully employed by previous work~\cite{Cui2020, Sarode2019} to track objects using point-cloud inputs. However, results showed that the architecture was a poor fit for our application. Siamese networks work best when the two input samples are largely similar and contain only small variations. This limitation is observed in object tracking networks where the Siamese encoder fails to track fast-deforming objects~\cite{Cui2020}. Since the shape inputs to CSG-CRN change drastically between cascades, the Siamese encoder fails to converge and encode the difference in shape data.

Rather than relying on an encoder network to find the differences and similarities between the target and initial reconstruction shapes, the final design of CSG-CRN represents this information with manually created input features. Details on the pre-processing step for computing the missing, filled, and excess volumes are described in the \nameref{sec:input_shape_representation} section. The six-dimensional input vector is encoded by a modified version of PointNet that is capable of ingesting multiple distance values in addition to the standard $R^3$ point inputs.


\section{CSG-Primitive~Prediction}
\label{sec:csg_primitive_prediction}

To predict a CSG primitive, we optimize for the function
\[f_\theta (X, Y) = (p, s, t, q, \alpha, \gamma).\]
We optimize the network parameters $\theta$, given an input point cloud $X$ and initial reconstruction point cloud $Y$. The model predicts the parameters of a primitive: primitive shape $p$, scale $s$, translation $t$, quaternion rotation $q$, blending factor $\alpha$, and boolean operation $\gamma$.


\section{CSG-To-SDF~Conversion}
\label{sec:csg_to_sdf_conversion}

Each primitive is represented by an SDF function. We can apply boolean operations to the primitive SDF functions to build a complete SDF function. The union of SDF functions $A$ and $B$ is computed as $min(A, B)$. A subtracted from B is computed as $min(-A, B)$. And the intersect of A and B is computed as $max(A, B)$.

To complete the refined CSG reconstruction, we combine the predicted primitive with the initial reconstruction SDF function using the predicted boolean operation. The refined reconstruction SDF can then sampled to compute the loss.


\section{Reconstruction~Loss}
\label{sec:reconstruction_loss}

We use the DeepSDF loss function to compute the reconstruction error between a target and a reconstruction point cloud. The DeepSDF loss function uses an L1 loss function with clamped SDF values
\[\Loss_{\surface}=\Loss_1(\clamp(\SDF(X)), \clamp(\SDF(Y))),\]
where $\clamp(x)$ is defined as $\max(-\delta, \min(\delta, x))$ for a clamping size $\delta$. We choose this loss function because it focuses the network on surface reconstruction quality. With clamping, the network would tend to minimize the average distance to the predicted primitive over all points. Unlike in DeepSDF, we uniformly sample points in a volume around the input shape. This makes it unlikely for points to be on the clamping boundary, which is not differentiable.

Because the loss function is clamped, the gradient is zero for primitives far from the object surface. We use an auxiliary loss from CSGStump to draw primitives to the reconstruction surface
\[\Loss_{\primitive} = \frac{1}{K} \sum_{k}^{K} \min ( \SDF_k^2(x_n) ).\]
The combined loss function is
\[\Loss_{\total} = \Loss_{\surface} + \Loss_{\primitive}.\]


\section{Cascaded~Refinement}
\label{sec:cascaded_refinement}

Once we have refined the reconstruction, we can sample another point cloud from the reconstruction and feed it back into the network. We again uniformly sample the SDF function.


\section{Training}
\label{sec:training}

We use a progressive training method inspired by Curriculum DeepSDF. In the first phase, all the initial reconstructions are empty. We represent this by representing the initial reconstruction as a single point at the origin. After training for a set number of epochs, we synthesize refined reconstructions and add them to the dataset. The second phase will randomly select samples from the initial and synthesized datasets. This process continues until the reconstructions reach a threshold accuracy. With this scheme, we train the model to refine partial reconstruction. And model can learn more efficiently by starting with easier samples and progressing to harder ones.
